Classless Java: Tuning Java Interfaces

### 2015-11-26 paper/sections/RelatedWork.tex
revising related work

\subsection{Meta-programming Competes with Language Extensions}
\bruno{needs to be polished better, I think}
\bruno{Mention/Compare with Language Virtualization work in Scala. They also re-interpret 
syntax.}
The most obvious solution to adding features to a language is language
extension.  It is often implemented as syntactic extensions that can be
desugared to the base language. For example, the Scala compiler was extended to
directly supports XML syntax. However, this approach does not support combining
multiple extensions into one. We are de facto creating a fork in the language,
and rarely the new fork gain enough traction to become the main language
release.  On this topic we mention SugarJ~\cite{erdweg11sugarj} - a Java-based
extensible language allowing programmers to extend it with custom features by
definitions in meta-DSLs (SDF, Stratego, etc).\bruno{so, what's the point that 
we want to make with SugarJ?}

@@

Here (compile/load time) code generation comes at the rescue: if for a certain
feature (\mixin in our case) it is possible to use the original language syntax
to \emph{express-describe} any specific instantiation of such feature
(annotating a class and provide getters), then we can insert in the compilation
process a tool that examins and enrichs the code before compilation. No need to
modify the original source; for example we can work on temporary files
\yanlin{Here what does temporary files mean? could explain more?}. Java is
a particular good candidate for this kind of manipulation since it already
provide ways to define and integrate such tools in its own compilation process:
in this way there is no need of temporary files, and there is a well defined way
of putting multiple extensions together.

>>>>

\subsection{Meta-programming Competes with Language Extensions}
\bruno{needs to be polished better, I think}
\bruno{Mention/Compare with Language Virtualization work in Scala. They also re-interpret 
syntax.}
The most obvious solution to adding features to a language is language
extension.  It is often implemented as syntactic extensions that can be
desugared to the base language. For example, the Scala compiler was extended to
directly supports XML syntax. However, this approach does not support combining
multiple extensions into one. We are de facto creating a fork in the language,
and rarely the new fork gain enough traction to become the main language
release.  On this topic we mention SugarJ~\cite{erdweg11sugarj} - a Java-based
extensible language allowing programmers to extend it with custom features by
definitions in meta-DSLs (SDF, Stratego, etc).\bruno{so, what's the point that 
we want to make with SugarJ?}\yanlin{we were talking about lightweight language
sugar, so SugarJ is a comparison to ours. Where using SugarJ requires learning
various DSLs like SDF, stratego, etc, in comparison, our approach is just using
Java. }

@@

Here (compile/load time)\yanlin{only compile time should do?} code generation comes at the rescue: if for a certain
feature (\mixin in our case) it is possible to use the original language syntax
to \emph{express-describe} any specific instantiation of such feature
(annotating a class and provide getters), then we can insert in the compilation
process a tool that examins and enrichs the code before compilation. No need to
modify the original source; for example we can work on temporary files
\yanlin{Here what does temporary files mean? could explain more?}. Java is
a particular good candidate for this kind of manipulation since it already
provide ways to define and integrate such tools in its own compilation process:
in this way there is no need of temporary files, and there is a well defined way
of putting multiple extensions together.
